---
title: "Simulation Exercise"
author: "Nick Orka"
date: "10/29/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
set.seed(19730509)
```

## Overview

In this project you will investigate the exponential distribution in R and compare it with the Central Limit Theorem.

## Simulations

```{r sumulation}
lambda <- 0.2
vals <- 40
n <- 1000
distr <- matrix(data = rexp(vals * n, lambda), nrow = n)
distr_means <- data.frame(means = apply(distr, 1, mean))
```
```{r echo=FALSE}
# plot the means
g <- ggplot(data = distr_means) + 
  geom_histogram(binwidth=0.1, mapping = aes(x=means), size=1) +   
  scale_x_continuous(breaks=round(seq(min(distr_means$means), max(distr_means$means), by=1))) + 
  labs(x = "Sample Means")
```

### Sample vs. Theoretical mean

```{r t_mean, echo=FALSE}
t_mu <- 1 / lambda
s_mu <- mean(distr_means$means)
print(paste(s_mu, "vs.", t_mu))
```

```{r echo=FALSE}
g + geom_vline(xintercept = t_mu, colour = "blue", size = 3) +
  annotate("text", x = t_mu, y=-2, hjust = -0.1, label = "Theoretical Mean")
```

### Sample vs. Theoretical variance

``` {r variance, echo=FALSE}
t_sd <- 1 / lambda / sqrt(vals)
s_sd <- sd(distr_means$means)
t_var <- t_sd ^ 2
s_var <- s_sd ^ 2
paste("Sample vs. Theoretical standard deviation is", s_sd, "vs.", t_sd)
paste("Sample vs. Theoretical standard variance is", s_var, "vs.", t_var)
```
As you can see the standard deviations are very close
Since variance is the square of the standard deviations, minor differnces will we enhanced, but are still pretty close.

### Distribution

Comparing the population means & standard deviation with a normal distribution of the expected values. Added lines for the calculated and expected means

```{r echo=FALSE, warning=FALSE}
# plot the means
ggplot(data = distr_means, aes(x = means)) + 
  geom_histogram(binwidth=0.1, aes(y=..density..), alpha=0.2) + 
  geom_vline(xintercept = t_mu, size=1, colour="#CC0000") + 
  geom_density(colour="blue", size=1) +
  geom_vline(xintercept = s_mu, size=1, colour="#0000CC") + 
  scale_x_continuous(breaks=seq(t_mu-3,t_mu+3,1), limits=c(t_mu-3,t_mu+3)) + 
  stat_function(fun = dnorm, args = list(mean = t_mu , sd = t_sd), colour = "red", size=1)
```

As you can see from the graph, the calculated distribution of means of random sampled exponantial distributions, overlaps quite nice with the normal distribution with the expected values based on the given lamba