---
title: "Basic Inferential Data Analysis"
author: "Nick Orka"
date: "10/29/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
```
## Data description
The response is the length of odontoblasts (cells responsible for tooth growth) in 60 guinea pigs. Each animal received one of three dose levels of vitamin C (0.5, 1, and 2 mg/day) by one of two delivery methods, orange juice or ascorbic acid (a form of vitamin C and coded as VC).

```{r summary}
str(ToothGrowth)
summary(ToothGrowth)
```
It looks like there are two dimensions (supplement and dosage) and one meassurement (length). Let's take a look at the groups combinations:
```{r groupping, echo = FALSE}
aggr <- ToothGrowth %>% group_by(supp, dose) %>% summarise(subj_count = n(), mu = mean(len, na.rm = TRUE), sd = sd(len, na.rm = TRUE))
aggr
```
```{r plot, echo=FALSE, warning=FALSE}
g <- ggplot(data = aggr) +
  geom_line(aes(x=dose, y=mu, color=supp), size=2, label = "mu") +
  geom_line(aes(x=dose, y=mu-sd, color=supp, label = "min sd")) +
  geom_line(aes(x=dose, y=mu+sd, color=supp, label = "max sd")) 
g
```

## Null Hypotesis - The supplement is more irrelevant the bigger dosage is.

```{r datasets}
OJ05 <- filter(ToothGrowth, supp == "OJ" & dose == 0.5)
OJ10 <- filter(ToothGrowth, supp == "OJ" & dose == 1.0)
OJ20 <- filter(ToothGrowth, supp == "OJ" & dose == 2.0)
VC05 <- filter(ToothGrowth, supp == "VC" & dose == 0.5)
VC10 <- filter(ToothGrowth, supp == "VC" & dose == 1.0)
VC20 <- filter(ToothGrowth, supp == "VC" & dose == 2.0)
```

### Dose 0.5

```{r t_test_05}
t.test(OJ05$len, VC05$len)
```

### Dose 1.0

```{r t_test_10}
t.test(OJ10$len, VC10$len)
```

### Dose 2.0

```{r t_test_20}
t.test(OJ20$len, VC20$len)
```

## Conclustion

As we can see Dose 0.5 and Dose 1.0 have significant difference in teeth growth with p_values 0.0064 and 0.001 respectively. But picture totally changes for Dose 2.0 where it’s doesn’t matter what supplements we are using the progress is pretty similar with p-value 0.934. The supplement used for the teeth grows is less relevant the bigger dosage. OJ gives more precise result with less variance then VC.
